The expected shape of the Milky Way's Dark Matter halo

### 2018-09-27 Paper/paper.tex
references
edit

If one wants to make a numerical study of the DM halo shape for the
MW, there is the additinal challenge of making a simulation that
resemble the observed properties of the MW disk.
All these difficulties (enough numerical resolution, explicit
cosmological context, appropriate feedback physics to produce
realistic MW disks) have limited the studies that want to study the
rounding effect of baryons in MW-like galaxies.

In this work we overcome these three limitation by analyzing the
Our objective is to quantify the DM halo shape and investigate the
effect of baryons.

%Better connector with observations of distant galaxies. Gravitational
%lensing and star tracers. (Talk about discrepancy with simulations,
%perhaps later) and state that the preference for axisymmetrical shapes
%may arise from the observational restrictions (projection) look for
%citations about this.

@@

@@

\section{Numerical Simulations}
In this work we use the results of the state-of-the art Auriga
simulations \cite{auriga}. It selected a set of 30 isolated halos from
the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
project \cite{Eagle}. Each halo was identified with the algorithm
"Friend of Friends" (FOF) \cite{Davis_et_al._1985}, which recursively
links particles if they are closer than some threshold distance
referred as linking length. EAGLE follows the evolution of fixed-mass
particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from
$z=127$ to $z=0$, adopting the $\Lambda$CDM model from the
\cite[Planck Collaboration et al. (2014)]{Planck_Collaboration_2014},
which is characterized by $\Omega_\Lambda=0.693$,
$\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \&
$\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.

These halos were randomly selected from a sample of the most isolated
quartile of halos whose virial mass $M_{200}$ varied between
$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. \textbf{\tiny This mass
  is defined as the mass enclosed within the virial radius $R_{200}$
  at which the density becomes 200 times the critical density of the
  universe. \huge FOOTNOTE \normalsize}. These halos were re-simulated
with the (AREPOOO HERE) by increasing the mass resolution of the
particles belonging to them and diminishing the resolution of the rest
of the particles.

Various versions of each halo were modelled with different degrees of
realism. All 30 halos were simulated within a level-4-degree of
resolution defined for Aquarius simulations corresponding to $\tilde
3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5
M_\odot$. The principal details of each of these halos are consigned
on the table \ref{tab:level4}. From these halos, 6 of them where
re-simulated at level 3 (higher) resolution taking into account a
spatial factor of 2 in each dimension. For more information about
level 3 halos, their details are printed on table
\ref{tab:level3}. Furthermore, fore each halo in each level of
resolution there are two versions of the simulation. One of tracks the
evolution of DM-only particles while the remaining one evolves DM and
baryions with magneto-hydrodynamical (MHD) physics, including DM.

>>>>

If one wants to make a numerical study of the DM halo shape for the
MW, there is the additinal challenge of making a simulation that
resemble the observed properties of the MW disk.
Recently \cite{2018arXiv180907255C} made a study in a cosmological
simulation to compare the effect of including baryons. They do find,
on average, rounder halo shapes once hydrodynamic effects are
included, but it is uncertain the strenght of this statistical effect
on galaxies similar to the MW.

All these difficulties (enough numerical resolution, explicit
cosmological context, appropriate feedback physics to produce
realistic MW disks) have limited the studies that want to study the
rounding effect of baryons in MW-like galaxies.
In this work we overcome these three limitation by analyzing the
results of state-of-the-art hydrodynamical simulations of isolated
halos that resemble the Milky Way.

@@

\section{Numerical Simulations}

In this work we use the results of the state-of-the art Auriga
simulations \cite{auriga}. 
The sample starts with a set of 30 isolated halos from the Evolution
and Assembly of GaLaxies and their Environments (EAGLE) project \cite{Eagle}. 
These halos were randomly selected from a sample of the most isolated
quartile of halos whose virial mass $M_{200}$ (200 times the critical
density of the Universe) varied between $10^{12}M_\odot$ and $2\cdot
10^{12}M_\odot$.
These halos were re-simulated with the moving mesh code AREPO
\citep{arepo} using different degrees of resolution and physics.
All 30 halos were simulated within a level-4-degree of
resolution defined for Aquarius simulations corresponding to $\sim
3\times 10^6$ high resolution particles of mass $\sim 2.5 \times 10^5
M_\odot$. 
%The principal details of each of these halos are consigned
%on the table \ref{tab:level4}. 
From these halos, 6 were re-simulated at a higher resolution (Level-3)
by increasing the number of particles by a factor of $8$.
For each ach halo in Level-3 and Level-4 there are two version: one
only includes DM particles, while the other also includes baryons with
magneto-hydrodynamicl (MHD) physics.
%re-simulated at level 3 (higher) resolution taking into account a
%spatial factor of 2 in each dimension. For more information about
%level 3 halos, their details are printed on table
%\ref{tab:level3}.

@@
